Query Optimization for Dynamic Imputation

### 2017-05-15 paper/relatedwork.tex
reword of yang

\review{
\textcite*{yang2015lenses} develops an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators, called Lenses. These can be used
to repair missing values by imposing data constraints such as \texttt{NOT NULL}. 
As with \ProjectName{}, they provide a way to balance between the quality of the cleaning 
performed (expressed by the confidence of their output) and the cost of those operations. However, their 
repairs take place on a per-tuple basis, with the non-deterministic layer of their system replacing place-holder
variables with inferred values. In contrast, \ProjectName{} optimizes imputation at the plan-level and
provides the same impute technique for all tuples streaming through a given operator.
}

>>>>

\review{
\textcite*{yang2015lenses} develops an incremental approach to ETL data cleaning, through the use
of probabilistic compositional repair operators, called \emph{Lenses}, which balance quality of cleaning
and cost of those operations. These operators can be used
to repair missing values by imposing data constraints such as \texttt{NOT NULL}. However, the model
used to impute missing values must be pre-trained and all repairs are done on a per-tuple basis
rather than at the plan-level.
}
